\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{0.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{0.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
\label{fig:1a_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
\label{fig:1b_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
\label{fig:2a_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}
